---
title: "Activities in a Store"
author: "Gabriel Martins Dias"
date: "07/05/2015"
output: html_document
---

```{r setup, include=FALSE}
# cache the code chucks in order to speed up the creation
knitr::opts_chunk$set(cache=TRUE)

# load libraries
library(ggplot2)
library(xlsx)
library(jsonlite)
library(manipulate)
library(lubridate)
library(caret)
library(plyr)
library(xtable)
```

# Summary

```{r, echo = FALSE}
ds1 <- read.xlsx("data/carreras/data.xlsx", sheetIndex = 1)

# interpret the JSON part
ds1.json <- mapply(fromJSON, as.character(ds1$productdata))
```

In this report we will study the activities in a store.

# Data Cleaning

First, we clean the data using the following code:
```{r}
ds1.json <- lapply(ds1.json, function(list.item){ 
                data.frame(colour.name = list.item$colour$name, 
                           colour.code = list.item$colour$code)
        } )
ds1.df <- do.call(rbind, ds1.json)

# add a new column
ds1.df$productid <- ds1$productid
ds1.df$skuid <- ds1$skuid

rownames(ds1.df) <- 1:nrow(ds1)
ds1 <- ds1.df
```

The cleaned data is the following set of rows:
```{r, echo = FALSE}
head(ds1, 20)
```

---

# Which Product is the Most Wanted?

To calculate this we used the following code:

```{r}
# the number of sales per product
tries <- tapply(ds1$skuid, ds1$productid, length)

# the product with more tries
tries[which(tries == max(tries))]
```

The most tried product is `r tries[which(tries == max(tries))]`.

---

# Which Combination is the Most Tried?

To calculate this we used the following code:

```{r}
# number of sales per product and color
tries <- tapply(ds1$skuid, ds1[, c("productid", "colour.code")], length)

# the product with more sales
ind <- which(tries == max(tries, na.rm = TRUE), arr.ind=TRUE)
```

One of the most tried combinations is the product `r (rownames(tries)[ind[1,2]])` with color
<span style="color:`r (colnames(tries)[ind[1,2]])`;">`r (colnames(tries)[ind[1,2]])`</span>.
